Patient-Specific Neural Field Modeling from Mirco-Electrode Data

### 2010-07-19 ltx/data_paper/DataPaper.tex
minor edit to paper and added bib file

\title{Patient-Specific Neural Field Model}
\author{In no specific order: Parham Aram, Dean Freestone, Kenneth Scerri, Michael Dewar,\\
 Jacob Donoghue, Sydney Cash, David Grayden and Visakan Kadirkamanathan  }

@@

\subsection{Estimating Support For Connectivity Kernel}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/CrossCorr2D.eps}
\end{center}
\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}. Note: The correlations are normalised such that the maximum value is one. A. Pre-seizure observation correlations. B. Seizure observation correlations. C. Post-seizure observation correlations.}
\label{fig:SpatialCrossCorrelation}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/HomoTestCrossCorr.eps}
\end{center}
\caption{{\bf Mean cross-correlations between subsets of the consecutive observations of the neural field}.}
\label{fig:HomogeneityTest}
\end{figure}

>>>>

\title{Patient-Specific Neural Field Modeling from Mirco-Electrode Data}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Jacob A. Donoghue, Sydney S. Cash, David B. Grayden and Visakan Kadirkamanathan  }

@@

\subsection{Estimating Support For Connectivity Kernel}
The support for the connectivity kernel can be inferred...

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/CrossCorr2D.eps}
\end{center}
\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}. Note: The correlations are normalised such that the maximum value is one. A. Pre-seizure observation correlations. B. Seizure observation correlations. C. Post-seizure observation correlations.}
\label{fig:SpatialCrossCorrelation}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/HomoTestCrossCorr.eps}
\end{center}
\caption{{\bf Mean cross-correlations between consecutive samples using subsets of observations of the neural field}. Each subplot shows correlations corresponding to a subset electrodes. Indexing the electrodes in a (x,y) grid, where index ranges from 1 to 10. Subplot A shows the mean correlation between electrode indexes (1-6, 5-10), subplot B shows correlations from indexes (5-10,5-10), subplot C shows indexes (1-6, 1-6) and subplot D shows indexes (5-10, 5-10).}
\label{fig:HomogeneityTest}
\end{figure}
